Supporting Information for ``The dynamics of starvation and recovery''

### 2017-02-09 Manuscript/12.tex
new yield constants

\usepackage{pnastwof}

@@

\bibliography{aa_starving3}

>>>>

\usepackage{pnastwoF}

@@

%\bibliography{aa_starving3}

\begin{thebibliography}{10}

\bibitem{Martin:1987dl}
Martin TE
\newblock (1987) {Food as a Limit on Breeding Birds: A Life-History
  Perspective}.
\newblock \emph{Annu. Rev. Ecol. Syst.} 18:453--487.

\bibitem{Kirk:1997cc}
Kirk KL
\newblock (1997) {Life-History Responses to Variable Environments: Starvation
  and Reproduction in Planktonic Rotifers}.
\newblock \emph{Ecology} 78:434--441.

\bibitem{Kempes:2012hy}
Kempes CP, Dutkiewicz S, Follows MJ
\newblock (2012) {Growth, metabolic partitioning, and the size of
  microorganisms.}
\newblock \emph{PNAS} 109:495--500.

\bibitem{Mangel:1988uaa}
Mangel M, Clark CW
\newblock (1988) \emph{{Dynamic Modeling in Behavioral Ecology}}
\newblock (Princeton University Press, Princeton).

\bibitem{Mangel:2014kz}
Mangel M
\newblock (2014) {Stochastic dynamic programming illuminates the link between
  environment, physiology, and evolution}.
\newblock \emph{B. Math. Biol.} 77:857--877.

\bibitem{Yeakel:2013hi}
Yeakel JD, Dominy NJ, Koch PL, Mangel M
\newblock (2014) {Functional morphology, stable isotopes, and human evolution:
  a model of consilience}.
\newblock \emph{Evolution} 68:190--203.

\bibitem{Morris:1987eo}
Morris DW
\newblock (1987) {Optimal Allocation of Parental Investment}.
\newblock \emph{Oikos} 49:332.

\bibitem{Tveraa:2003fq}
Tveraa T, Fauchald P, Henaug C, Yoccoz NG
\newblock (2003) {An examination of a compensatory relationship between food
  limitation and predation in semi-domestic reindeer}.
\newblock \emph{Oecologia} 137:370--376.

\bibitem{Daan:1988va}
Daan S, Dijkstra C, Drent R, Meijer T
\newblock (1988) \emph{{Food supply and the annual timing of avian
  reproduction}}.

\bibitem{Jacot:2009dv}
Jacot A, Valcu M, van Oers K, Kempenaers B
\newblock (2009) {Experimental nest site limitation affects reproductive
  strategies and parental investment in a hole-nesting passerine}.
\newblock \emph{Animal Behaviour} 77:1075--1083.

\bibitem{Stearns:1989ip}
Stearns SC
\newblock (1989) {Trade-Offs in Life-History Evolution}.
\newblock \emph{Funct. Ecol.} 3:259.

\bibitem{Barboza:2002in}
Barboza P, Jorde D
\newblock (2002) {Intermittent fasting during winter and spring affects body
  composition and reproduction of a migratory duck}.
\newblock \emph{J Comp Physiol B} 172:419--434.

\bibitem{Threlkeld:1976ih}
Threlkeld ST
\newblock (1976) {Starvation and the size structure of zooplankton
  communities}.
\newblock \emph{Freshwater Biol.} 6:489--496.

\bibitem{Weber:1998jg}
Weber TP, Ens BJ, Houston AI
\newblock (1998) {Optimal avian migration: A dynamic model of fuel stores and
  site use}.
\newblock \emph{Evolutionary Ecology} 12:377--401.

\bibitem{Mduma:1999cp}
Mduma SAR, Sinclair ARE, Hilborn R
\newblock (1999) {Food regulates the Serengeti wildebeest: a 40-year record}.
\newblock \emph{J. Anim. Ecol.} 68:1101--1122.

\bibitem{Moore:2014hi}
Moore JW, Yeakel JD, Peard D, Lough J, Beere M
\newblock (2014) {Life-history diversity and its importance to population
  stability and persistence of a migratory fish: steelhead in two large North
  American watersheds}.
\newblock \emph{J. Anim. Ecol.} 83:1035--1046.

\bibitem{Mead:1989dt}
Mead RA
\newblock (1989) in \emph{Carnivore Behavior, Ecology, and Evolution}
\newblock (Springer US, Boston, MA), pp 437--464.

\bibitem{Sandell:1990kw}
Sandell M
\newblock (1990) {The Evolution of Seasonal Delayed Implantation}.
\newblock \emph{The Quarterly Review of Biology} 65:23--42.

\bibitem{Bulik:1999eo}
Bulik CM, {et~al.}
\newblock (1999) {Fertility and Reproduction in Women With Anorexia Nervosa}.
\newblock \emph{J. Clin. Psychiatry} 60:130--135.

\bibitem{Trites:2003cc}
Trites AW, Donnelly CP
\newblock (2003) {The decline of Steller sea lions Eumetopias jubatus in
  Alaska: a review of the nutritional stress hypothesis}.
\newblock \emph{Mammal Review} 33:3--28.

\bibitem{Glazier:2009hq}
Glazier DS
\newblock (2009) {Metabolic level and size scaling of rates of respiration and
  growth in unicellular organisms}.
\newblock \emph{Funct. Ecol.} 23:963--968.

\bibitem{Kooi2000}
Kooijman SALM
\newblock (2000) \emph{{Dynamic Energy and Mass Budgets in Biological Systems}}
\newblock (Cambridge).

\bibitem{Sousa:2010ez}
Sousa T, Domingos T, Poggiale JC, Kooijman SALM
\newblock (2010) {Dynamic energy budget theory restores coherence in biology}.
\newblock \emph{Philos. T. Roy. Soc. B} 365:3413--3428.

\bibitem{Diekmann:2010da}
Diekmann O, Metz JAJ
\newblock (2010) {How to lift a model for individual behaviour to the
  population level?}
\newblock \emph{Philos. T. Roy. Soc. B} 365:3523--3530.

\bibitem{murdoch:2003}
Murdoch WW, Briggs CJ, Nisbet RM
\newblock (2003) \emph{{Consumer-resource Dynamics}}, Monographs in population
  biology
\newblock (Princeton University Press).

\bibitem{Benichou:2014wu}
Benichou O, Redner S
\newblock (2014) {Depletion-Controlled Starvation of a Diffusing Forager}.
\newblock \emph{arXiv}.

\bibitem{Benichou:2016wl}
B{\'e}nichou O, Chupeau M, Redner S
\newblock (2016) {Role of Depletion on the Dynamics of a Diffusing Forager}.

\bibitem{Chupeau:2016jf}
Chupeau M, B{\'e}nichou O, Redner S
\newblock (2016) {Universality classes of foraging with resource renewal}.
\newblock \emph{Phys. Rev. E} 93:032403.

\bibitem{murray2011mathematical}
Murray JD
\newblock (2011) \emph{{Mathematical Biology: I. An Introduction}},
  Interdisciplinary Applied Mathematics
\newblock (Springer New York, Melaka Manipal Medical College (Manipal Campus),
  International Centre for Health Sciences, Madhav Nagar, Manipal, Udupi
  District, Karnataka State, India. nayaksathish@yahoo.com) Vol.{} 110.

\bibitem{Strogatz:2008wo}
Strogatz SH
\newblock (2008) \emph{{Nonlinear Dynamics and Chaos}}, With Applications to
  Physics, Biology, Chemistry, and Engineering
\newblock (Westview Press).

\bibitem{GuckHolmes}
Guckenheimer J, Holmes P
\newblock (1983) \emph{{Nonlinear oscillations, dynamical systems, and
  bifurcations of vector fields}}
\newblock (Springer, New York).

\bibitem{Gross:2004p2428}
Gross T, Feudel U
\newblock (2004) {Analytical search for bifurcation surfaces in parameter
  space}.
\newblock \emph{Physica D} 195:292--302.

\bibitem{Hastings:2001jh}
Hastings A
\newblock (2001) {Transient dynamics and persistence of ecological systems}.
\newblock \emph{Ecol. Lett.} 4:215--220.

\bibitem{Neubert:1997wk}
Neubert M, Caswell H
\newblock (1997) {Alternatives to resilience for measuring the responses of
  ecological systems to perturbations}.
\newblock \emph{Ecology} 78:653--665.

\bibitem{Caswell:2005eo}
Caswell H, Neubert MG
\newblock (2005) {Reactivity and transient dynamics of discrete-time ecological
  systems}.
\newblock \emph{Journal of Difference Equations and Applications} 11:295--310.

\bibitem{Neubert:2009td}
Neubert M, Caswell H
\newblock (2009) {Detecting reactivity}.
\newblock \emph{Ecology}.

\bibitem{Yodzis:1992hg}
Yodzis P, Innes S
\newblock (1992) {Body Size and Consumer-Resource Dynamics}.
\newblock \emph{Am. Nat.} 139:1151--1175.

\bibitem{Brown:2004wq}
Brown J, Gillooly J, Allen A, Savage V, West G
\newblock (2004) {Toward a metabolic theory of ecology}.
\newblock \emph{Ecology} 85:1771--1789.

\bibitem{West:2002it}
West GB, Woodruff WH, Brown JH
\newblock (2002) {Allometric scaling of metabolic rate from molecules and
  mitochondria to cells and mammals.}
\newblock \emph{Proc. Natl. Acad. Sci. USA} 99 Suppl 1:2473--2478.

\bibitem{DeLong:2010dy}
DeLong JP, Okie JG, Moses ME, Sibly RM, Brown JH
\newblock (2010) {Shifts in metabolic scaling, production, and efficiency
  across major evolutionary transitions of life.}
\newblock \emph{PNAS} 107:12941--12945.

\bibitem{West:2001bv}
West GB, Brown JH, Enquist BJ
\newblock (2001) {A general model for ontogenetic growth}.
\newblock \emph{Nature} 413:628--631.

\bibitem{moses2008rmo}
Moses ME, {et~al.}
\newblock (2008) {Revisiting a Model of Ontogenetic Growth: Estimating Model
  Parameters from Theory and Data}.
\newblock \emph{http://dx.doi.org.proxy.lib.sfu.ca/10.1086/679735}
  171:632--645.

\bibitem{gillooly2002esa}
Gillooly JF, Charnov EL, West GB, Savage VM, Brown JH
\newblock (2002) {Effects of size and temperature on developmental time}.
\newblock \emph{Nature} 417:70--73.

\bibitem{hou}
Hou C, {et~al.}
\newblock (2008) {Energy Uptake and Allocation During Ontogeny}.
\newblock \emph{Science} 322:736--739.

\bibitem{bettencourt}
Bettencourt LMA, Lobo J, Helbing D, Kuhnert C, West GB
\newblock (2007) {Growth, innovation, scaling, and the pace of life in cities}.
\newblock \emph{Proc. Natl. Acad. Sci. USA} 104:7301--7306.

\bibitem{Folland:2008ij}
Folland JP, Mc~Cauley TM, Williams AG
\newblock (2008) {Allometric scaling of strength measurements to body size}.
\newblock \emph{Eur J Appl Physiol} 102:739--745.

\bibitem{CalderIII:1983jd}
Calder~III WA
\newblock (1983) {An allometric approach to population cycles of mammals}.
\newblock \emph{J. Theor. Biol.} 100:275--282.

\bibitem{Peterson:1984hj}
Peterson RO, PAGE RE, DODGE KM
\newblock (1984) {Wolves, Moose, and the Allometry of Population Cycles}.
\newblock \emph{Science} 224:1350--1352.

\bibitem{Krukonis:1991fk}
Krukonis G, Schaffer WM
\newblock (1991) {Population cycles in mammals and birds: Does periodicity
  scale with body size?}
\newblock \emph{J. Theor. Biol.} 148:469--493.

\bibitem{Hendriks:2012fc}
Hendriks AJ, Mulder C
\newblock (2012) {Delayed logistic and Rosenzweig{\textendash}MacArthur models
  with allometric parameter setting estimate population cycles at lower trophic
  levels well}.
\newblock \emph{Ecological Complexity} 9:43--54.

\bibitem{Kendall:1999iy}
Kendall BE, {et~al.}
\newblock (1999) {Why do populations cycle? A synthesis of statistical and
  mechanistic modeling approaches}.
\newblock \emph{Ecology} 80:1789--1805.

\bibitem{Hogstedt:2005cr}
H{\"o}gstedt G, Seldal T, Breistol A
\newblock (2005) {Period length in cyclic animal populations}.
\newblock \emph{Ecology} 86:373--378.

\bibitem{Kendall:1998hl}
Kendall, Prendergast, Bjornstad
\newblock (1998) {The macroecology of population dynamics: taxonomic and
  biogeographic patterns in population cycles}.
\newblock \emph{Ecol. Lett.} 1:160--164.

\bibitem{Brown:1993p708}
Brown J, Marquet P, Taper M
\newblock (1993) {Evolution of body size: consequences of an energetic
  definition of fitness}.
\newblock \emph{Am. Nat.} 142:573--584.

\bibitem{West:1997cg}
West GB, Brown JH, Enquist BJ
\newblock (1997) {A General Model for the Origin of Allometric Scaling Laws in
  Biology}.
\newblock \emph{Science} 276:122--126.

\bibitem{West:2002ud}
West GB, Woodruff WH, Brown JH
\newblock (2002) {Allometric scaling of metabolic rate from molecules and
  mitochondria to cells and mammals}.
\newblock \emph{Proc. Natl. Acad. Sci. USA} 99:2473--2478.

\bibitem{Millar:1990p923}
Millar J, Hickling G
\newblock (1990) { Fasting Endurance and the Evolution of Mammalian Body Size}.
\newblock \emph{Funct. Ecol.} 4:5--12.

\bibitem{Alroy:1998p1594}
Alroy J
\newblock (1998) {Cope's rule and the dynamics of body mass evolution in North
  American fossil mammals}.
\newblock \emph{Science} 280:731.

\bibitem{Clauset:2009fh}
Clauset A, Redner S
\newblock (2009) {Evolutionary Model of Species Body Mass Diversification}.
\newblock \emph{Phys. Rev. Lett.} 102:038103.

\bibitem{Smith:2010p3442}
Smith F, Boyer A, Brown J, Costa D
\newblock (2010) {The Evolution of Maximum Body Size of Terrestrial Mammals}.
\newblock \emph{Science}.

\bibitem{Saarinen:2014br}
Saarinen JJ, {et~al.}
\newblock (2014) {Patterns of maximum body size evolution in Cenozoic land
  mammals: eco-evolutionary processes and abiotic forcing}.
\newblock \emph{Proc Biol Sci} 281:20132049--20132049.

\bibitem{allen2002}
Allen AP, Brown JH, Gillooly JF
\newblock (2002) {Global Biodiversity, Biochemical Kinetics, and the
  Energetic-Equivalence Rule}.
\newblock \emph{Science} 297:1545--1548.

\bibitem{enquist1998}
Enquist BJ, Brown JH, West GB
\newblock (1998) {Allometric scaling of plant energetics and population density
  : Abstract : Nature}.
\newblock \emph{Nature} 395:163--165.

\bibitem{tilman1981}
Tilman D
\newblock (1981) {Tests of Resource Competition Theory Using Four Species of
  Lake Michigan Algae}.
\newblock \emph{Ecology} 62:802--815.

\bibitem{dutkiewicz2009}
Dutkiewicz S, Follows MJ, Bragg JG
\newblock (2009) {Modeling the coupling of ocean ecology and biogeochemistry}.
\newblock \emph{Global Biogeochem. Cycles} 23:n/a--n/a.

\bibitem{barton2010}
Barton AD, Dutkiewicz S, Flierl G, Bragg J, Follows MJ
\newblock (2010) {Patterns of Diversity in Marine Phytoplankton}.
\newblock \emph{Science} 327:1509--1511.

\end{thebibliography}

### 2017-02-09 Manuscript/Yield-Constants-Calculation-2.tex
new yield constants

>>>>

\section*{Explicit Consumption Derivation}
If I were to write out an explicit mass balance for our system in a dimensional system it would be:
\begin{align} 
\begin{split}
\dot{F} &= \lambda\left(R\right) F + \rho\left(R\right)H - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho\left(R\right)H - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho\left(R\right)}{Y}+P\right)H+\left(\frac{\lambda\left(R\right)}{Y}+P\right)F\right]
\end{split}
\end{align}
(note this is not fully explicit because I don't know how to deal with the response of $\sigma$ to resources, although I have an idea for a derivation which may be necessary given the following approximations), where $\lambda\left(R\right)$ and $\rho\left(R\right)$ are the growth and recovery functions dependent on resource availability. Typically these can be written as $\lambda\left(R\right)=\lambda_{max}S\left(R\right)$ where $\lambda_{max}$ is the maximum growth rate which changes with size, and $S\left(R\right)$ is a saturating function of resources, for example a Michealis-Menten or Monod function of the form $\frac{R}{k_{H}+R}$.  In these equations $Y$ represents the quantity of resources required to build a unit of organism (e.g. gram of mammal produced per gram of grass consumed) and $P$ is the specific maintenance rate of resource consumption (g resource $\cdot$ s$^{-1}$ $\cdot$ g organism). If we pick $F$ and $H$ to have units of (g organisms $\cdot$ m$^{-2}$), then terms like $\frac{\rho\left(R\right)}{Y}H$ have units of (g resource $\cdot$ m$^{-2}$ $\cdot$ s$^{-1}$) which is just the net primary productivity (NPP), a natural unit for $\dot{R}$, and this also gives us the units of $R$ as (g $\cdot$ m$^{-2}$) which is also a natural unit and is just the biomass density. In this system of units $\alpha$ is the growth rate of $R$. First, before diving into the constant values and a general nondimensionalization, let's look at the limits of the above equations in relationship to our two-state model: The saturation function should be defined by a linear regime proportional to $R$ when $R<<k$ and a constant value for $R>>k$. Thus for starving individuals, where $R<<k$, we have that $\rho\left(R\right)=\rho_{max}R/k$, and for the full class or organisms $\lambda\left(R\right)=\lambda_{max}$ such that the above relationships reduce to
\begin{align} 
\begin{split}
\dot{F} &= \lambda_{max} F + \rho_{max}RH/k - \sigma \left(1-\frac{R}{C}\right)F,  \\
\dot{H} &= \sigma \left(1-\frac{R}{C}\right)F - \rho_{max}R H/k - \mu H,  \\
\dot{R} &= \alpha R\left(1-\frac{R}{C}\right) -\left[\left(\frac{\rho_{max}R}{Yk}+P\right)H+\beta F\right]
\end{split}
\end{align}
where $\beta=\frac{\lambda_{max}}{Y}+P$ which is just a constant that depends on the size of an organisms via the allometries for $\lambda_{max}$ and $P$.

Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
\begin{align} 
\begin{split}
\dot{F}^{*} &= \frac{1}{s}\left[\lambda_{max} F^{*} + \rho_{max}\frac{R^{*}}{qk}H^{*} - \sigma \left(1-\frac{R^{*}}{qC}\right)F^{*}\right],  \\
\dot{H}^{*} &= \frac{1}{s}\left[\sigma \left(1-\frac{R^{*}}{qC}\right)F^{*} - \rho_{max}\frac{R^{*}}{qk} H^{*} - \mu H^{*}\right],  \\
\dot{R}^{*} &= \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left[\left(\frac{\rho_{max}R^{*}}{Ykq}+P\right)H^{*}+\beta F^{*}\right]\right]
\end{split}
\end{align}
Now there is a choice of factors that provides us with our original set of equations: if we pick $s=1$, $q=1/C$, and $f=1/Yk$, then we are left with 
\begin{align} 
\begin{split}
\dot{F}^{*} &= \lambda_{max} F^{*} + \rho_{2}R^{*}H^{*} - \sigma \left(1-R^{*}\right)F^{*},  \\
\dot{H}^{*} &= \sigma \left(1-R^{*}\right)F^{*} - \rho_{2} R^{*}H^{*} - \mu H^{*},  \\
\dot{R}^{*} &= \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{2}R^{*}+P_{2}\right)H^{*}-\beta_{2} F^{*}
\end{split}
\end{align}
where $\rho_{2}=C\rho_{max}/k$, $P_{2}=YkP/C$, and $\beta_{2}=Yk\beta/C$. Typically the value of $C/k$ should roughly be $2$. A summary of the parameters values is then: $\rho_{2}=$ 2 times our old $\rho$; $\lambda$, $\sigma$, and $\mu$ are all unchanged (the max notation can be dropped here and equated with the old values). Now $P=B_{0}m^{3/4}$, and $Y=18200$ (J g$^{-1}$) for grass \cite{estermann} which allows us to calculate $P_{2}=YB_{0}m^{3/4}/2$ and $\beta_{2}=Y/2$ (note again that $\beta=\frac{\lambda_{max}}{Y}+P$, and $\lambda_{max}$ is our old value for $\lambda$) . Finally, the value of $\alpha$ is given by the NPP divided by the corresponding biomass densities which I find to be $\alpha=2.10\times10^{-9}$ (s$^{-1}$) in a database that I have.

%
% term reduces to $\rho_{max}/k_{H}RH$ which is what we had before except that $\rho_{max}$ has an extra constant in it. For full individuals,  $R>>k$ and the $\lambda_{max}\frac{R}{k_{F}+R} F$ term becomes simply $\lambda_{max}F$ which differs from our previous version of the last term in the third equation. We are justified in taking both of these limits at the same time because of how we are binning and defining nutritional state (Note: we can simulate the full dynamics with the $\frac{R}{k+R}$ terms and see how different things are).

%Now consider the following nondimensionalization (ignoring the $\sigma (1-R)F$ terms which I don't have a dimensional form for yet),: $F^{*}=fF$, $H^{*}=fH$, $R^{*}=qR$, $t^{*}=st$ then we would have:
%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &= \frac{1}{s}\left(\lambda_{max}\frac{R^{*}}{k_{F}q+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}\right),  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  \frac{1}{s}\left(- \rho_{max}\frac{R^{*}}{k_{H}q+R^{*}}H^{*} - \mu H^{*}\right),  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \frac{1}{s}\left[\alpha R^{*}\left(1-\frac{R^{*}}{qC}\right) -\frac{q}{f}\left(\frac{\rho_{max}}{Y}\frac{R^{*}}{k_{H}q+R^{*}}H^{*}+\frac{\lambda_{max}}{Y}\frac{R^{*}}{k_{F}q+R^{*}}F^{*}\right)\right].
%\end{split}
%\end{align}

%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}} F^{*} + \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*},  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  - \rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*} - \mu H^{*},  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\rho_{max}\frac{R^{*}}{k_{H}/C+R^{*}}H^{*}+\lambda_{max}\frac{R^{*}}{k_{F}/C+R^{*}}F^{*}\right).
%\end{split}
%\end{align}
%and taking the above limits we have 
%\begin{align} 
%\begin{split}
%\frac{\partial F^{*}}{\partial t^{*}} &=\lambda_{max}F^{*} + \frac{\rho_{max}C}{k_{H}}R^{*}H^{*},  \\
%\frac{\partial H^{*}}{\partial t^{*}} &=  - \frac{\rho_{max}C}{k_{H}}R^{*}H^{*} - \mu H^{*},  \\
%\frac{\partial R^{*}}{\partial t^{*}} &=  \alpha R^{*}\left(1-R^{*}\right) -\left(\frac{\rho_{max}C}{k_{H}}R^{*}H^{*}+\lambda_{max}F^{*}\right).
%\end{split}
%\end{align}
%In summary, this is exactly our original system of equations (again with a $\lambda F$ instead of a $\lambda RF$ term in the last equation; and without dealing with the $\sigma (1-R)F$ term) and the only modification is that $\rho$ is adjusted by a factor of $C/k_{H}$ which should just be equal to $2$, and $F^{*}$, $H^{*}$, and $R^{*}$ are unites.

%Now let us return to the third equation which is the last place where we need to define constants slightly more mechanistically. In the dimensional version we would have the following:
%\begin{equation}
%\label{Rprime}
%\dot{R^{\prime}} = \alpha^{\prime} R^{\prime}\left(1-\frac{R^{\prime}}{C}\right) - \delta^{\prime} \left(\frac{\rho_{max}}{Y}\frac{R^{\prime}}{k_{H}^{\prime}+R^{\prime}}H+\frac{\lambda_{max}}{Y}\frac{R^{\prime}}{k_{F}^{\prime}+R^{\prime}}F\right).
%\end{equation}
%If we pick $R^{\prime}$ to have units of (g $\cdot$ m$^{-2}$) then $C$ is the maximum biomass density (g $\cdot$ m$^{-2}$), and $\alpha^{\prime}$ will have units of s$^{-1}$. Nondimensionalizing 
%as $R=R^{\prime}/C$ then leads to $\alpha=\alpha^{\prime}C$ with units of (g $\cdot$ m$^{-2}$ s$^{-1}$) such that the $\alpha$ in our system of equations can simply be treated as the net primary productivity (NPP). The second term of Equation \ref{Rprime} is mostly unaffected by the nondimensionalization except that the $k\equiv k^{\prime}/C$. Now $\alpha$ in our model is just the externally provided NPP values ranging between $1.59\times10^{-6}$ and $7.92\times10^{-5}$ (g s$^{-1}$ m$^{-2}$) where we can take $3\times10^{-5}$ (g s$^{-1}$ m$^{-2}$) as a typical value.

%Now $\rho_{max}/Y$ and $\lambda_{max}/Y$ both have units of (g R $\cdot$ s$^{-1}$ $\cdot$ g Organism $^{-1}$) and thus the unit of $\delta^{\prime}$ must be (g organism $\cdot$ Individuals $^{-1}$ $\cdot$ m$^{-2}$)
